The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-25 science_ms.tex
Removed quiet and intense halo paragraph labels.  This wouldn't work with the unlabeled sections in Science.

\textit{Quiet halo}.--- Afterwards an equilbrium of $[\bar{Z}_2/H]
\sim -2.5$ is established between metal-rich outflows and metal-poor
inflows.  Galactic outflows are directed in the polar directions of
the gas disk, keeping the adjacent filaments metal-poor.  These
features and a well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are
apparent in the metallicity projections in Figure
\ref{fig:projections}.  The average stellar metallicity is within 0.5
dex of $[\bar{Z}_2/H]$.

\textit{Intense halo}.--- The first few Pop II star clusters have
$[Z/H]$ between --1 and --2 and dominate the average stellar
metallicity at $z > 8$.  Afterwards the metallicity increases by a
factor of 30 to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a
starburst.  Because this halo is located in a large-scale overdensity,
most of the ejecta falls back into the halo after reaching distances
up to 20 comoving kpc, in turn keeping the halo gas metallicity high
because the inflows are relatively metal-rich themselves.  After the
$z \sim 8$ starburst, the average stellar metallicity follows the
average gas metallicity within 0.1 dex.

@@

\textit{Quiet halo}.--- The most massive progenitor interestingly
never hosts a Pop III star.  Instead a nearby halo forms a Pop III
star, which (randomly) produces a PISNe at $z=16$.  The blastwave
overruns the most massive progenitor, and the dense core survives this
event and is enriched by this PISN, triggering the transition to Pop
II SF.  Other progenitors host three Pop III stars, forming at $z =
15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
from these two PISNe and Pop II SF quench Pop III SF in this halo.

\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
halo's progenitors until $z=9$ when most of these halos enter the
metal-rich bubble surrounding the intense halo.  There are two stars
forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
enriched by external blastwaves that only partially enriched the dense
regions.  This falls into the metallicity range where fragmentation
could occur if dust cooling is efficient below \tento{-4} $Z_\odot$.
The most massive progenitors of the intense halo cease to form Pop III
stars at $z<12$ because of nearby or intrinsic PISNe.

@@

\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from an
isolated system with the stellar feedback steadily enriching the ISM,
resulting in a correlation between stellar age and metallicity.  After
$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
discussed in \S\ref{sec:zevo}.  The SFR peaks at $z=10$ and decreases
as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
merger occurs, and the gas inside the satellite halo is compressed,
triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
This halo infalls through a filament, where most of metal enrichment
in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
disk and filament.  The filament and thus this satellite halo remains
relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
of the total stellar mass.

\textit{Intense halo}.--- In contrast with the quiet halo, the intense
halo undergoes a few mergers of halos with an established stellar
population.  This creates a superposition of age-metallicity tracks in
the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
two Pop II stellar clusters have an unexpectedly high metallicity
[Z/H] $\sim$ --1, which occurs when a PISN blastwave triggers SF in
two neighboring halos.  Most of the early SF have [Z/H] = --2.5.  At
$z=9$, the halo's virial temperature reaches \tento{4} K.  This
combined with a 10:1 merger creates a starburst that quickly enriches
the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
itself with further SF until $z=7$.  The spikes in the scatter plot
correspond to SN triggered SF in nearby molecular clouds that are
enriched up to a factor of 10 with respect to the ISM.  However their
mass fraction are small compared to the total stellar mass.  The
starburst at $z=9$ creates a bimodal metallicity distribution with
peaks at [Z/H] = --2.4 and --1.2 with the metal-rich component mainly
being created after the starburst.  Two systems with sizable stellar
components merge into the halo at $z \sim 8$, and their stellar
populations are still discernible in the metallicity-age plot, whose
tracks are noted by dashed lines.  Stars with [Z/H] $<$ --3 compose
1.8 percent of the total stellar mass.

>>>>

In the quiet halo, an equilbrium of $[\bar{Z}_2/H] \sim -2.5$ is
established between metal-rich outflows and metal-poor inflows.
Galactic outflows are directed in the polar directions of the gas
disk, keeping the adjacent filaments metal-poor.  These features and a
well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are apparent in the
metallicity projections in Figure \ref{fig:projections}.  The average
stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.

In the intense halos, the first few Pop II star clusters have $[Z/H]$
between --1 and --2 and dominate the average stellar metallicity at $z
> 8$.  Afterwards the metallicity increases by a factor of 30 to
$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
Because this halo is located in a large-scale overdensity, most of the
ejecta falls back into the halo after reaching distances up to 20
comoving kpc, in turn keeping the halo gas metallicity high because
the inflows are relatively metal-rich themselves.  After the $z \sim
8$ starburst, the average stellar metallicity follows the average gas
metallicity within 0.1 dex.

@@

The most massive progenitor of the quiet halo interestingly never
hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
the most massive progenitor, and the dense core survives this event
and is enriched by this PISN, triggering the transition to Pop II SF.
Other progenitors host three Pop III stars, forming at $z = 15.4,
14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
these two PISNe and Pop II SF quench Pop III SF in this halo.

The progenitors of the intense halo host a total of 56 Pop III stars
with 21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$
halo at $z=19$.  Pop III stars form on a regular interval in the
halo's progenitors until $z=9$ when most of these halos enter the
metal-rich bubble surrounding the intense halo.  There are two stars
forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
enriched by external blastwaves that only partially enriched the dense
regions.  This falls into the metallicity range where fragmentation
could occur if dust cooling is efficient below \tento{-4} $Z_\odot$.
The most massive progenitors of the intense halo cease to form Pop III
stars at $z<12$ because of nearby or intrinsic PISNe.

@@

A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 in the
quiet halo at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from an
isolated system with the stellar feedback steadily enriching the ISM,
resulting in a correlation between stellar age and metallicity.  After
$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
previously discussed.  The SFR peaks at $z=10$ and decreases as the
cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger
occurs, and the gas inside the satellite halo is compressed,
triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
This halo infalls through a filament, where most of metal enrichment
in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
disk and filament.  The filament and thus this satellite halo remains
relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
of the total stellar mass.

In contrast with the quiet halo, the intense halo undergoes a few
mergers of halos with an established stellar population.  This creates
a superposition of age-metallicity tracks in the SFH, seen in the
complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
occurs when a PISN blastwave triggers SF in two neighboring halos.
Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
temperature reaches \tento{4} K.  This combined with a 10:1 merger
creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
$z=8$.  The halo continues to enrich itself with further SF until
$z=7$.  The spikes in the scatter plot correspond to SN triggered SF
in nearby molecular clouds that are enriched up to a factor of 10 with
respect to the ISM.  However their mass fraction are small compared to
the total stellar mass.  The starburst at $z=9$ creates a bimodal
metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
the metal-rich component mainly being created after the starburst.
Two systems with sizable stellar components merge into the halo at $z
\sim 8$, and their stellar populations are still discernible in the
metallicity-age plot, whose tracks are noted by dashed lines.  Stars
with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.
